### 2014-04-29 doc/coppermtn_multilevel/tech_report/multilevel_mc.tex
fixing broken references in multilevel mc note

Next we perform the same calculations using the adjoint Monte Carlo
solver presented in \cite{evans_monte_2012}. Before doing this
however, we must first modify the linear problem as the Monte Carlo
solver is a direct method and therefore a homogeneous problem with a
right hand side of $\ve{0}$ will yield no samples. Instead, we will
solve the residual problem:
\begin{equation}
  \ve{A}\ve{d} = \ve{r}\:,
  \label{eq:residual_problem}
\end{equation}
where the residual of the homogeneous problem is:
\begin{equation}
  \ve{r} = -\ve{A}\ve{x}^0\:,
  \label{eq:homogenous_residual}
\end{equation}
and the solution is computed as:
\begin{equation}
  \ve{x} = \ve{x}^0 + \ve{d}\:.
  \label{eq:residual_solution}
\end{equation}
Forming the problem in this way lets us directly apply the adjoint
Monte Carlo method to the homogeneous problem and then apply the
effective correction, $\ve{d}$, to the initial guess to give the
solution. This approach is also equivalent to performing a single
iteration of Halton's method \cite{halton_sequential_1962}. Using this
formulation we can again solve the model problem with wave numbers of
1, 5 and 10 on a grid of size $J = 100$ but this time we vary the
number of histories used to compute the solution instead of the number
of iterations. Figure~\ref{fig:adjoint_mc} gives the results of these
calculations.
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=4in]{adjoint_mc.png}
  \end{center}
  \caption{\textbf{Convergence of the adjoint Monte Carlo method as a
      function of sampled histories for a grid of size $J = 100$.}
    \textit{Adjoint Monte Carlo performs better for smaller wave
      numbers and therefore smoother modes.}}
  \label{fig:adjoint_mc}
\end{figure}
Surprisingly, the Monte Carlo method performs better for smooth modes
than more oscillatory modes\footnote{This behavior was also observed
  for the forward Monte Carlo method presented in
  \cite{evans_monte_2012}.}. The results of these calculations are
counterintuitive given the fact that the Monte Carlo solver is
effectively a stochastic realization of Richardson's iteration and
therefore one should expect the same spectral behavior from the
results.

Looking at the timing results in Table~\ref{tab:mc_timing}, we see
that the behavior of the Monte Carlo solver is in fact consistent with
these expectations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cc}\hline\hline
      \multicolumn{1}{c}{\textbf{Wave Number}} & 
      \multicolumn{1}{c}{\textbf{Time per History (s)}} \\
      \hline
      1 & 1 \\
      5 & 0.85 \\
      10 & 0.83 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Normalized average CPU time per history.}}
  \label{tab:mc_timing}
\end{table}
Timing results show that the average time required to compute an
entire history in the Monte Carlo solver decreases as a function of
wave number. We showed analytically in \cite{slattery_2013} that the
length of the random walk is equivalent to the number of Richardson
iterations that would be required to achieve a given convergence
criteria. In Figure~\ref{fig:richardson}, we see that fewer iterations
are required to converge larger wave numbers and therefore we should
also expect shorter random walks in the Monte Carlo solver and
therefore a faster time to solution as observed in
Table~\ref{tab:mc_timing}. However, this does not indicate why the
Monte Carlo solvers perform better for smoother modes rather than
oscillatory modes. Fortunately, the explanation for this behavior is
simple. Consider the plots for the Fourier modes with $k = 1$ and $k =
10$ given in Figure~\ref{fig:fourier_modes}.
\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{mode_1.pdf}
    \caption{\textbf{Fourier mode with $k = 1$.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{mode_10.pdf}
    \caption{\textbf{Fourier mode with $k = 10$.}}
  \end{subfigure}
  \caption{\textit{The more oscillatory the mode the finer the
      structure of the error. Finer structures require more samples to
      resolve them.}}
  \label{fig:fourier_modes}
\end{figure}
The higher the wave number is the more oscillatory the mode
appears. To resolve these fine structures in the error we therefore
naturally require more Monte Carlo samples to distinguish them from
one another. In other words, statistical noise in the solution must be
reduced by more samples in order to resolve fine structures in the
error that would otherwise be buried in the noise.

@@

\clearpage

@@

\subsection{Heterogeneous Results}
We next solve the same linear problem as before using $M=2$ but this
time with a constant forcing of $\ve{b}=1.0$ such that:
\begin{equation}
  \ve{A}\ve{x} = \ve{b}\:.
  \label{eq:heterogeneous_problem}
\end{equation}
We will choose an initial guess of $\ve{0}$ for these calculations as
the solution is non-trivial and fix $N$ at 10,000 while increasing the
number of levels. Table~\ref{tab:heterogeneous_fixed_t} gives the
results of these calculations. Here the relative error error
calculations were computed using an exact solution computed using a
minimal residual iteration converged to a residual norm tolerance of
$\sn{1}{-12}$.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cllllllll}\hline\hline
      \multicolumn{1}{c}{\textbf{Levels}} &
      \multicolumn{1}{l}{\textbf{Samples}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{Time (s)}} &
      \multicolumn{1}{l}{\textbf{RRESFOM}} &
      \multicolumn{1}{l}{\textbf{RERRFOM}} \\
      \hline
      1 & 10,000 & 0.025 & 0.223 & 0.241 & 2.97 & 6.77 & 1.0 & 1.0 \\
      2 & 17,596 & 0.044 & 0.339 & 0.277 & 5.49 & 7.19 & 0.31 & 0.71 \\
      3 & 29,571 & 0.050 & 0.365 & 0.131 & 1.66 & 7.21 & 0.23 & 3.18 \\
      4 & 53,295 & 0.062 & 0.483 & 0.081 & 0.96 & 7.29 & 0.16 & 8.28 \\
      5 & 92,301 & 0.086 & 0.662 & 0.105 & 0.88 & 7.13 & 0.08 & 5.00 \\
      6 & 185,266 & 0.120 & 0.891 & 0.102 & 0.72 & 7.10 & 0.04 & 5.32 \\
      7 & 355,543 & 0.069 & 0.513 & 0.056 & 0.51 & 6.92 & 0.13 & 18.12 \\
      8 & 742,337 & 0.093 & 0.654 & 0.081 & 0.67 & 7.07 & 0.07 & 8.47 \\
      9 & 1,624,121 & 0.122 & 0.758 & 0.107 & 0.83 & 7.08 & 0.04 &
      4.85 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Coarse grid results for $\ve{b} = 1$ with $M = 2$,
      $t \approx 7s$ and run times reported in seconds.}
    \textit{RRESSFOM values are the relative figure of merit computed
      using the infinity norm of the residual. RERRFORM values are the
      relative figure of merit computed using the infinity norm of the
      absolute error vector.}}
  \label{tab:heterogeneous_coarse_grids}
\end{table}

Based on the residual norm values, it would seem as though the 1 level
result was superior as better convergence was achieved in the same
amount of compute time using residual norm metrics. However, the
structure of the actual solutions would indicate
otherwise. Figure~\ref{fig:heterogeneous_ml_solutions} gives the
results for with 1-9 levels all plotted against the exact
solution. Clearly, the estimate produced by the 9 level computation is
more representative of the exact solution than the single level scheme
as indicated by the error norms due to the well-converged results
provided coarse level estimates. Furthermore, the error norms also
indicate a more efficient solution scheme when multiple levels are
used showing similar relative figure of merit metrics for the error
norm computations.

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_1_level.pdf}
    \caption{\textbf{1 level.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_2_level.pdf}
    \caption{\textbf{2 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_3_level.pdf}
    \caption{\textbf{3 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_4_level.pdf}
    \caption{\textbf{4 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_5_level.pdf}
    \caption{\textbf{5 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_6_level.pdf}
    \caption{\textbf{6 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_7_level.pdf}
    \caption{\textbf{7 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_8_level.pdf}
    \caption{\textbf{8 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_9_level.pdf}
    \caption{\textbf{9 levels.}}
  \end{subfigure}
  \caption{\textbf{Solution of the Poisson problem using the geometric
      multilevel Monte Carlo method with 1-9 levels and approximately
      7 seconds of compute time.} \textit{Increasing the number of
      levels in the computation improves convergence with respect to
      the relative solution error but convergence with respect to the
      linear problem residual is worse.}}
  \label{fig:heterogenous_fixed_t}
\end{figure}

@@

%%---------------------------------------------------------------------------%%
\section{Coarse Grid Monte Carlo Acceleration}
Based on the above results we then consider using only the coarse grid
calculations as the acceleration. Consider the following results given
in Table~\ref{tab:heterogeneous_cg_solutions} where a coarse grid
solution has been produced at a fixed $N=10,000$ and then simply
prolongated back to the fine grid rather than solving all levels using
Algorithm~\ref{alg:mlamc}. Figure~\ref{fig:hetergeneous_cg_solutions}
plots the coarse grid solutions prolongated back to the fine grid
along with the exact solution. We see that as we coarsen the grid
while fixing $N$, the coarse grid statistics are better than the fine
grid as there is a larger ratio of samples to grid points. The result
is a very precise coarse grid result that when prolongated to the fine
grid simply incurs the grid error associated with the linear
interpolation.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cllllllll}\hline\hline
      \multicolumn{1}{c}{\textbf{Levels}} &
      \multicolumn{1}{l}{\textbf{Samples}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{Time (s)}} &
      \multicolumn{1}{l}{\textbf{RRESFOM}} &
      \multicolumn{1}{l}{\textbf{RERRFOM}} \\
      \hline
      1 & 10,000 & 0.025 & 0.223 & 0.241 & 2.97 & 6.77 & 1.0 & 1.0 \\
      2 & 10,000 & 0.012 & 0.067 & 0.303 & 6.05 & 3.29 & 9.70 & 1.3 \\
      3 & 10,000 & 0.005 & 0.028 & 0.133 & 1.70 & 1.62 & 103.6 & 13.7 \\
      4 & 10,000 & 0.004 & 0.013 & 0.058 & 0.61 & 0.81 & 292.7 & 146.3 \\
      5 & 10,000 & 0.023 & 0.031 & 0.141 & 3.06 & 0.40 & 20.8 & 49.4 \\
      6 & 10,000 & 0.006 & 0.008 & 0.051 & 0.77 & 0.20 & 557.0 & 741.1 \\
      7 & 10,000 & 0.006 & 0.006 & 0.049 & 0.77 & 0.10 & 1,103 & 1,589 \\
      8 & 10,000 & 0.009 & 0.009 & 0.022 & 0.29 & 0.05 & 952.8 & 15,329 \\
      9 & 10,000 & 0.013 & 0.014 & 0.032 & 0.51 & 0.03 & 997.9 &
      14,826 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Geometric Multilevel Monte Carlo results for
      $\ve{b} = 1$ with $M = 2$, $N = 10,000$ and run times reported
      in seconds.} \textit{RRESSFOM values are the relative figure of
      merit computed using the infinity norm of the residual. RERRFORM
    values are the relative figure of merit computed using the
    infinity norm of the absolute error vector.}}
  \label{tab:heterogeneous_cg_solutions}
\end{table}

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_1_level.pdf}
    \caption{\textbf{Level 1 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_2_level.pdf}
    \caption{\textbf{Level 2 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_3_level.pdf}
    \caption{\textbf{Level 3 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_4_level.pdf}
    \caption{\textbf{Level 4 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_5_level.pdf}
    \caption{\textbf{Level 5 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_6_level.pdf}
    \caption{\textbf{Level 6 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_7_level.pdf}
    \caption{\textbf{Level 7 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_8_level.pdf}
    \caption{\textbf{Level 8 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_9_level.pdf}
    \caption{\textbf{Level 9 solution.}}
  \end{subfigure}
  \caption{\textbf{Solution of the Poisson problem using the geometric
      multilevel Monte Carlo method with 1-9 levels and $N = 10,000$.}
    \textit{Coarse solutions prolongated to the fine grid give better
      results in less time than fine grid solutions.}}
  \label{fig:heterogenous_cg_solutions}
\end{figure}

>>>>

Next we perform the same calculations using the adjoint Monte Carlo
solver presented in \cite{evans_monte_2012}. Before doing this
however, we must first modify the linear problem as the Monte Carlo
solver is a direct method and therefore a homogeneous problem with a
right hand side of $\ve{0}$ will yield no samples. Instead, we will
solve the residual problem:
\begin{equation}
  \ve{A}\ve{d} = \ve{r}\:,
  \label{eq:residual_problem}
\end{equation}
where the residual of the homogeneous problem is:
\begin{equation}
  \ve{r} = -\ve{A}\ve{x}^0\:,
  \label{eq:homogeneous_residual}
\end{equation}
and the solution is computed as:
\begin{equation}
  \ve{x} = \ve{x}^0 + \ve{d}\:.
  \label{eq:residual_solution}
\end{equation}
Forming the problem in this way lets us directly apply the adjoint
Monte Carlo method to the homogeneous problem and then apply the
effective correction, $\ve{d}$, to the initial guess to give the
solution. This approach is also equivalent to performing a single
iteration of Halton's method \cite{halton_sequential_1962}. Using this
formulation we can again solve the model problem with wave numbers of
1, 5 and 10 on a grid of size $J = 100$ but this time we vary the
number of histories used to compute the solution instead of the number
of iterations. Figure~\ref{fig:adjoint_mc} gives the results of these
calculations.
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=4in]{adjoint_mc.png}
  \end{center}
  \caption{\textbf{Convergence of the adjoint Monte Carlo method as a
      function of sampled histories for a grid of size $J = 100$.}
    \textit{Adjoint Monte Carlo performs better for smaller wave
      numbers and therefore smoother modes.}}
  \label{fig:adjoint_mc}
\end{figure}
Surprisingly, the Monte Carlo method performs better for smooth modes
than more oscillatory modes\footnote{This behavior was also observed
  for the forward Monte Carlo method presented in
  \cite{evans_monte_2012}.}. The results of these calculations are
counterintuitive given the fact that the Monte Carlo solver is
effectively a stochastic realization of Richardson's iteration and
therefore one should expect the same spectral behavior from the
results.

Looking at the timing results in Table~\ref{tab:mc_timing}, we see
that the behavior of the Monte Carlo solver is in fact consistent with
these expectations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cc}\hline\hline
      \multicolumn{1}{c}{\textbf{Wave Number}} & 
      \multicolumn{1}{c}{\textbf{Time per History (s)}} \\
      \hline
      1 & 1 \\
      5 & 0.85 \\
      10 & 0.83 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Normalized average CPU time per history.}}
  \label{tab:mc_timing}
\end{table}
Timing results show that the average time required to compute an
entire history in the Monte Carlo solver decreases as a function of
wave number. We showed analytically in \cite{slattery_2013} that the
length of the random walk is equivalent to the number of Richardson
iterations that would be required to achieve a given convergence
criteria. In Figure~\ref{fig:richardson}, we see that fewer iterations
are required to converge larger wave numbers and therefore we should
also expect shorter random walks in the Monte Carlo solver and
therefore a faster time to solution as observed in
Table~\ref{tab:mc_timing}. However, this does not indicate why the
Monte Carlo solvers perform better for smoother modes rather than
oscillatory modes. Fortunately, the explanation for this behavior is
simple. Consider the plots for the Fourier modes with $k = 1$ and $k =
10$ given in Figure~\ref{fig:fourier_modes}.
\begin{figure}[t!]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{mode_1.pdf}
    \caption{\textbf{Fourier mode with $k = 1$.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{mode_10.pdf}
    \caption{\textbf{Fourier mode with $k = 10$.}}
  \end{subfigure}
  \caption{\textit{The more oscillatory the mode the finer the
      structure of the error. Finer structures require more samples to
      resolve them.}}
  \label{fig:fourier_modes}
\end{figure}
The higher the wave number is the more oscillatory the mode
appears. To resolve these fine structures in the error we therefore
naturally require more Monte Carlo samples to distinguish them from
one another. In other words, statistical noise in the solution must be
reduced by more samples in order to resolve fine structures in the
error that would otherwise be buried in the noise.

@@

@@

\subsection{Heterogeneous Results}
We next solve the same linear problem as before using $M=2$ but this
time with a constant forcing of $\ve{b}=\ve{1}$ such that:
\begin{equation}
  \ve{A}\ve{x} = \ve{b}\:.
  \label{eq:heterogeneous_problem}
\end{equation}
We will choose an initial guess of $\ve{x}^0 = \ve{0}$ for these
calculations as the solution is non-trivial and fix $N$ at 10,000
while increasing the number of
levels. Table~\ref{tab:heterogeneous_fixed_t} gives the results of
these calculations. Here the relative error error calculations were
computed using an exact solution computed using a minimal residual
iteration converged to a residual norm tolerance of $\sn{1}{-12}$.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cllllllll}\hline\hline
      \multicolumn{1}{c}{\textbf{Levels}} &
      \multicolumn{1}{l}{\textbf{Samples}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{Time (s)}} &
      \multicolumn{1}{l}{\textbf{RRESFOM}} &
      \multicolumn{1}{l}{\textbf{RERRFOM}} \\
      \hline
      1 & 10,000 & 0.025 & 0.223 & 0.241 & 2.97 & 6.77 & 1.0 & 1.0 \\
      2 & 17,596 & 0.044 & 0.339 & 0.277 & 5.49 & 7.19 & 0.31 & 0.71 \\
      3 & 29,571 & 0.050 & 0.365 & 0.131 & 1.66 & 7.21 & 0.23 & 3.18 \\
      4 & 53,295 & 0.062 & 0.483 & 0.081 & 0.96 & 7.29 & 0.16 & 8.28 \\
      5 & 92,301 & 0.086 & 0.662 & 0.105 & 0.88 & 7.13 & 0.08 & 5.00 \\
      6 & 185,266 & 0.120 & 0.891 & 0.102 & 0.72 & 7.10 & 0.04 & 5.32 \\
      7 & 355,543 & 0.069 & 0.513 & 0.056 & 0.51 & 6.92 & 0.13 & 18.12 \\
      8 & 742,337 & 0.093 & 0.654 & 0.081 & 0.67 & 7.07 & 0.07 & 8.47 \\
      9 & 1,624,121 & 0.122 & 0.758 & 0.107 & 0.83 & 7.08 & 0.04 &
      4.85 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Coarse grid results for $\ve{b} = 1$ with $M = 2$,
      $t \approx 7s$ and run times reported in seconds.}
    \textit{RRESSFOM values are the relative figure of merit computed
      using the infinity norm of the residual. RERRFORM values are the
      relative figure of merit computed using the infinity norm of the
      absolute error vector.}}
  \label{tab:heterogeneous_fixed_t}
\end{table}

Based on the residual norm values, it would seem as though the 1 level
result was superior as better convergence was achieved in the same
amount of compute time using residual norm metrics. However, the
structure of the actual solutions would indicate
otherwise. Figure~\ref{fig:heterogeneous_fixed_t} gives the
results for with 1-9 levels all plotted against the exact
solution. Clearly, the estimate produced by the 9 level computation is
more representative of the exact solution than the single level scheme
as indicated by the error norms due to the well-converged results
provided coarse level estimates. Furthermore, the error norms also
indicate a more efficient solution scheme when multiple levels are
used showing similar relative figure of merit metrics for the error
norm computations as those computed in the heterogeneous cases.

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_1_level.pdf}
    \caption{\textbf{1 level.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_2_level.pdf}
    \caption{\textbf{2 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_3_level.pdf}
    \caption{\textbf{3 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_4_level.pdf}
    \caption{\textbf{4 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_5_level.pdf}
    \caption{\textbf{5 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_6_level.pdf}
    \caption{\textbf{6 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_7_level.pdf}
    \caption{\textbf{7 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_8_level.pdf}
    \caption{\textbf{8 levels.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_9_level.pdf}
    \caption{\textbf{9 levels.}}
  \end{subfigure}
  \caption{\textbf{Solution of the Poisson problem using the geometric
      multilevel Monte Carlo method with 1-9 levels and approximately
      7 seconds of compute time.} \textit{Increasing the number of
      levels in the computation improves convergence with respect to
      the relative solution error but convergence with respect to the
      linear problem residual is worse. Numeric results from these
      calculations are given in
      Table~\ref{tab:heterogeneous_fixed_t}.}}
  \label{fig:heterogeneous_fixed_t}
\end{figure}

@@

%%---------------------------------------------------------------------------%%
\section{Coarse Grid Monte Carlo Acceleration}
Based on the above results we then consider using only the coarse grid
calculations as the acceleration. Consider the following results given
in Table~\ref{tab:heterogeneous_cg_solutions} where a coarse grid
solution has been produced at a fixed $N=10,000$ and then simply
prolongated back to the fine grid rather than solving all levels using
Algorithm~\ref{alg:mlamc}. Figure~\ref{fig:heterogeneous_cg_solutions}
plots the coarse grid solutions prolongated back to the fine grid
along with the exact solution. We see that as we coarsen the grid
while fixing $N$, the coarse grid statistics are better than the fine
grid as there is a larger ratio of samples to grid points. The result
is a very precise coarse grid result that when prolongated to the fine
grid simply incurs the grid error associated with the linear
interpolation.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cllllllll}\hline\hline
      \multicolumn{1}{c}{\textbf{Grid}} &
      \multicolumn{1}{l}{\textbf{Samples}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{r}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{\infty}$}} &
      \multicolumn{1}{l}{\textbf{$||\ve{e}||_{2}$}} &
      \multicolumn{1}{l}{\textbf{Time (s)}} &
      \multicolumn{1}{l}{\textbf{RRESFOM}} &
      \multicolumn{1}{l}{\textbf{RERRFOM}} \\
      \hline
      1 & 10,000 & 0.025 & 0.223 & 0.241 & 2.97 & 6.77 & 1.0 & 1.0 \\
      2 & 10,000 & 0.012 & 0.067 & 0.303 & 6.05 & 3.29 & 9.70 & 1.3 \\
      3 & 10,000 & 0.005 & 0.028 & 0.133 & 1.70 & 1.62 & 103.6 & 13.7 \\
      4 & 10,000 & 0.004 & 0.013 & 0.058 & 0.61 & 0.81 & 292.7 & 146.3 \\
      5 & 10,000 & 0.023 & 0.031 & 0.141 & 3.06 & 0.40 & 20.8 & 49.4 \\
      6 & 10,000 & 0.006 & 0.008 & 0.051 & 0.77 & 0.20 & 557.0 & 741.1 \\
      7 & 10,000 & 0.006 & 0.006 & 0.049 & 0.77 & 0.10 & 1,103 & 1,589 \\
      8 & 10,000 & 0.009 & 0.009 & 0.022 & 0.29 & 0.05 & 952.8 & 15,329 \\
      9 & 10,000 & 0.013 & 0.014 & 0.032 & 0.51 & 0.03 & 997.9 &
      14,826 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Coarse grid Monte Carlo results for
      $\ve{b} = 1$ with $M = 2$, $N = 10,000$ and run times reported
      in seconds.} \textit{RRESSFOM values are the relative figure of
      merit computed using the infinity norm of the residual. RERRFORM
    values are the relative figure of merit computed using the
    infinity norm of the absolute error vector.}}
  \label{tab:heterogeneous_cg_solutions}
\end{table}

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{7_sec_1_level.pdf}
    \caption{\textbf{Grid 1 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_2_level.pdf}
    \caption{\textbf{Grid 2 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_3_level.pdf}
    \caption{\textbf{Grid 3 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_4_level.pdf}
    \caption{\textbf{Grid 4 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_5_level.pdf}
    \caption{\textbf{Grid 5 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_6_level.pdf}
    \caption{\textbf{Grid 6 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_7_level.pdf}
    \caption{\textbf{Grid 7 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_8_level.pdf}
    \caption{\textbf{Grid 8 solution.}}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{cg_9_level.pdf}
    \caption{\textbf{Grid 9 solution.}}
  \end{subfigure}
  \caption{\textbf{Solution of the Poisson problem using geometric
      grids 1-9 and Monte Carlo with $N = 10,000$ for each
      calculation.} \textit{Coarse solutions prolongated to the fine
      grid give better results in less time than fine grid
      solutions. Numeric results for these calculations are given in
      Table~\ref{tab:heterogeneous_cg_solutions}.}}
  \label{fig:heterogeneous_cg_solutions}
\end{figure}
